Joint analysis of read count data

### 2020-09-09 combined_analysis/combine_all_data.Rmd
add zenith

@@

# SCZ by sex
L_SCZ = Lbase
L_SCZ['DxSCZ:Reported_GenderMale'] = 1
L_SCZ['Reported_GenderMale'] = -1
L_SCZ['DxSCZ'] = -1
L_SCZ['DxControl'] = 1 
# (A - B) - (C - D) = A - B - C + D

# BP by sex
L_BP = Lbase
L_BP['DxBP:Reported_GenderMale'] = 1
L_BP['Reported_GenderMale'] = -1
L_BP['DxBP'] = -1
L_BP['DxControl'] = 1

L = cbind(	SczSex = L_SCZ,
			BPSex = L_BP)

@@

```{r plots.interaction.DxSex, fig.width=10, fig.height=5}
# Disease
tab = topTable(fit_interaction_DxSex, "SczSex", number=Inf) %>% getGeneSymbol
fig1 = plotVolcano( tab, tab$Symbol[1:20] ) + ggtitle("SCZ")

@@

```{r gene_set_test.DxSex}
res_zenith_DxSex.GO = run_zenith( fit_interaction_DxSex, colnames(L), gs.GO.collection )
res_zenith_DxSex.MSigDB = run_zenith( fit_interaction_DxSex, colnames(L), gs.MSigDB.collection )
```

>>>>

METADATA$Reported_Gender = factor(METADATA$Reported_Gender)
METADATA$Dx = factor(METADATA$Dx, c("BP", "Control", "SCZ"))

@@

# SCZ by sex
L_SCZ = Lbase
L_SCZ['DxSCZ:Reported_GenderMale'] = 1
L_SCZ['DxControl:Reported_GenderMale"'] = -1
L_SCZ['DxSCZ'] = -1
L_SCZ['DxControl'] = 1 
# (A - B) - (C - D) = A - B - C + D

# # BP by sex
# L_BP = Lbase
# L_BP['DxBP:Reported_GenderMale'] = 1
# L_BP['Reported_GenderMale'] = -1
# L_BP['DxBP'] = -1
# L_BP['DxControl'] = 1

L = cbind(	SczSex = L_SCZ)#,
			# BPSex = L_BP)

@@

```{r plots.interaction.DxSex, fig.width=10, fig.height=5}
# Disease. 
tab = topTable(fit_interaction_DxSex, "SczSex", number=Inf) %>% getGeneSymbol
fig1 = plotVolcano( tab, tab$Symbol[1:20] ) + ggtitle("SCZ")

@@

```{r gene_set_test.DxSex}
res_zenith_DxSex.GO = run_zenith( fit_interaction_DxSex, colnames(L), gs.GO.collection ). 
res_zenith_DxSex.MSigDB = run_zenith( fit_interaction_DxSex, colnames(L), gs.MSigDB.collection )
```
